Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-15 paper.qmd
Saved updated mapping data
Removed unncessary chunks
Added the models only

@@

# write_rds(distance_df_small_edges, "data/five_gau_clusters/pacmap_wireframe.rds")
# write_rds(df_b, "data/five_gau_clusters/pacmap_model.rds")
```

>>>>

# write_rds(df_b, "data/five_gau_clusters/pacmap_model.rds")

@@

write_rds(distance_df_small_edges, "data/five_gau_clusters/pacmap_wireframe.rds")
# write_rds(df_b, "data/five_gau_clusters/pacmap_model.rds")
```

 ## Give unique values to hex IDs
 hexid_unique <- pacmap_data_with_hb_id |> 
   arrange(hb_id) |> 
   distinct(hb_id) |> 
   mutate(ID = row_number())

 ## Find points in each hex bin
 pts_df <- pacmap_data_with_hb_id |>
     group_by(hb_id) |>
     summarize(pts_list = list(ID), .groups = "drop")

 unlisted_df <- pts_df |>
   unnest(cols = pts_list) |>
   rename(pts_ID = pts_list)

 pts_df <- left_join(hexid_unique, unlisted_df, by = c("hb_id"))

 write_rds(pts_df, "data/five_gau_clusters/pacmap_model_mapping_data.rds")
```
